Project Light

### 2015-09-02 paper/paper.tex
formulate some paragraphs from the introduction

\iffalse
% this can be deleted later, just to have it in version control
As computers have gotten smaller and less demanding, they were not just used directly anymore, but also embedded into a larger mechanical or technical system (SOURCE!): they enabled new kinds of gadgets or at least improved them dramatically.
\textit{embedded systems} were born.they
\fi

The Internet of Things (IoT)...

- Internet of things is coming
- small connected devices (aka motes) work together to monitor and control from remote
- unconnected embedded system had large impact on daily lives already
- with networking, this impact will become greater
- many possibilities, prospects of success
- but: connected devices have much larger attack surface
- so security becomes way more important
- counter measures within network stack (akes) --> works great
- but: needs to be configured, which hard with limited i/o capabilities

- preloading in fabrics is kinda unsafe
- plugging is sophisticated for normal setups, because many devices involved

>>>>

The Internet of Things (IoT) is becoming more and more reality every day.
It consists of small devices (called \textit{motes}), which are connected to the public Internet.
They work together to allow us monitoring and controlling several kinds of real-world systems, % SOURCE!
e.g. motes collecting information about parking lot occupancy allowing drivers to find free spaces using their smart phones\footnote{see http://www.streetline.com/}.

In the last decades, the rise embedded systems changed our daily lives. % Source?
However, these systems often had limited networking capabilities or at least used their own, proprietary and thus unaccessible network technology.
Because of the huge variety if valuable possibilities, the impact of embedded systems will be advanced even further within the IoT.

However, this comes at a price: by being accessible from the Internet, the attack surface of such systems is much larger than traditional embedded system had to face.
New, adapted security measurements had to be developed and implemented to react to this.
For example, Adaptive Key Establishment Scheme (AKES) provides adaptable security measures for being used with the IEEE~802.15.4 network stack, which is commonly used by IoT devices. % SOURCE!
Nevertheless, one problem remains: IoT setups usually consist of plentiful nodes which all need to be initialized with keying material and parameters.
This is a major problem, because typical motes lack of input/output devices which are securely usable without configured networking.

One possibility is to plug a wire to each and every node in order to initialize it.
However, there are two downsides: first, a typical IoT setup consist of too many devices to be plugging a feasible solution. Second, attackers may have physical access to motes, so jacks on the mote (e.g. JTAG) are a dangerous security threat.

Another approach is to pre-initialize the keys in the factory.
This would mean that either there is a small set of assigned keys, which would lead to vulnerabilities to brute-force attacks; or each mote gets an individual key, which requires a secure transmission and attribution of keys to motes\footnote{This would also increase cost of motes. However, they need to be as cheap as possible in order to be be affordable in great numbers.}.
Anyway, pre-initialization requires somebody other than the user/installer to know the keys, which diminishes security.
